Data Specialization for a Staged Lambda Calculus

### 2014-11-07 paper/splitting.tex
more stage one splitting descriptions

\TODO REDO THE REST OF THE TEXT TO WALK THROUGH THE MAJOR RULES OF SPLITTING

In general, the

At stage \bbone\ {\tt case}s, the splitting rules adds injections to the precomputations of each branch. 
This is then cased in the resumer to resume the stage \bbtwo\ portion of the correct branch.
This rule and $\pause$ are the only two places where nontrivial information is added to the precomputation.

The goal of stage 2 splitting was to generate a precomputation and resumer such
that the resumer and the \lang\ residual reduce to the same final value.
However, stage~\bbone\ terms do not reduce to final values, rather they reduce
to residual tables and partial values.  
Therefore, to make the results of splitting match the
the partial value above, we choose to split \bbone\ terms in \lang\ into a
resumer that reduces to the same value as the stage~\bbtwo\ computation, and an
$e_1$ that not only performs the precomputation expected by the resumer, but
also computes values that match the stage~\bbone\ aspects of the partial value.

@@

The $\prev$ and $\pause$ rules depends on
splitting stage \bbone\ terms, and so they are covered later.

>>>>

When $e$ is a terminal (variable or base constant), the combined result
is formed by tupling $e$ with a \texttt{()} precomputation, 
and the resumer is just constant \texttt{()}.  
For example, \texttt{3} simply splits into combined result \texttt{((3,())} and \texttt{\_=>4}.
When $e$ is a non-terminal (except $\next$),
splitting descends into $e$, recursively splitting subterms
and generating combined terms $c_1,\ldots,c_n$.
The new combined term of $e$ then works by binding $c_1,\ldots,c_n$
to the patterns $(y_1,z_1),\ldots,(y_n,z_n)$
to isolate their immediate results and precomputations.
The immediate result of $e$ is then formed by replacing its subterms with $y_1,\ldots,y_n$, 
and the precomputation is formed from the tuple of $z_1,\ldots,z_n$.

At {\tt case}s, only one of the branches' combined results is executed, and its precomputation injected and bundled with the precomputation of the predicate. 
This precomputation is then cased in the resumer to resume the stage \bbtwo\ portion of the correct branch.
This rule and $\pause$ are the only two places where nontrivial information is added to the precomputation.

[FUNCTIONS]

@@

\subsection{Interface Rules}
